---
title: "Quick start guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick start guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

After successfully importing MsFPOP, we can identify changepoints within a singal 
by using the Ms.FPOP algorithm, through the function of the same name (``MsFPOP()``).
For this brief demonstration, the constants $\gamma=9$ and $\beta=2.25$ have been
calibrated based on simulations from Liehrmann and Rigaill 2023. The \textit{iid} Gaussian signal of variance 1 is affected by 2 changepoints occuring at position 
200 and 400. The mean values corresponding to the initial, intermediate, and final
segments are 0, $\sqrt{\frac{1}{6}}$, and 0 respectively.

```{r}
library(MsFPOP)
set.seed(1)
beta  <- 2.25
gamma <- 9
n     <- 600
mu    <- rep(c(0,sqrt(100/n),0), rep(200,3))
y     <- rnorm(n)+mu
cp    <- MsFPOP(y=y, beta=beta, alpha=gamma+beta*log(n))$changepoint
cp 
```


``MsFPOP()`` estimates two changepoints at positions 200 and 402. It should be noted 
that the latter position represents the overall signal length, a value that 
``MsFPOP()`` invariably returns.

# References 

Liehrmann, A. and Rigaill, G. Ms.Fpop: An Exact and Fast Segmentation
Algorithm With a Multiscale Penalty (2023) [doi:10.48550/arXiv.2303.08723](https://doi.org/10.48550/arXiv.2303.08723).
